Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-17 analysis2_manuscript.tex
Update analysis2_manuscript.tex

    \subsection*{Quality control and software development}
    Following the protocol established previously for other aspects of \stdpopsim{} \citep{adrion2020community},
    new DFEs are subjet to a rigorous quality control (QC) process,
    by which a separate individual re-implements the same DFE, and the two implementations
    are programatically tested for equality.
    The QC process identified a substantial bug in one DFE:
    the \textit{Drosophila melanogaster} DFE \texttt{LognormalPlusPositive\_R16} \citet{booker2021selective}.
    Due to an error in coding the log-normal distribution, deleterious selection coefficients
    were several orders of magnitude too large.
    The bug affected results in a separate project from one of our groups
    that made use of this DFE before QC had been done.
    All changes and additions to the code must pass a comprehensive set of unit tests:
    at the time of writing, the library includes over 11,000 lines of testing code,
    that run 2,862 unit tests, including comparisons to QC implementations
    and cross-checks for agreement, including between \slim and \msprime implementations of the same models.
    For instance, for testing we make use of \slim's scriptability to separately record in simulation metadata
    information about current population sizes, DFEs, etcetera,
    which are then programmatically compared to the models used to generate the \slim script
    that ran the simulation.
    We make use of automatic test ``code coverage'' tools to help ensure that all portions of the code base
    are validated by these unit tests.

>>>>

    \subsection*{Quality control and software development}
    Following the protocol established previously for other aspects of \stdpopsim{} \citep{adrion2020community},
    new DFEs are subjet to a rigorous quality control (QC) process,
    by which a separate individual re-implements the same DFE, and the two implementations
    are programatically tested for equality.
    The QC process identified a substantial bug in one DFE:
    the \textit{Drosophila melanogaster} DFE \texttt{LognormalPlusPositive\_R16} \citet{booker2021selective}.
    Due to an error in coding the log-normal distribution, deleterious selection coefficients
    were several orders of magnitude too large.
    The bug affected results in a separate project from one of our groups
    that made use of this DFE before QC had been done.
    All changes and additions to the code must pass a comprehensive set of unit tests:
    at the time of writing, the library includes over 11,000 lines of testing code,
    that run 2,862 unit tests, including comparisons to QC implementations
    and cross-checks for agreement, including between \slim and \msprime implementations of the same models.
    For instance, for testing we make use of \slim's scriptability to separately record in-simulation metadata
    information about current population sizes, DFEs, etcetera,
    which are then programmatically compared to the models used to generate the \slim script
    that ran the simulation.
    We make use of automatic test ``code coverage'' tools to help ensure that all portions of the code base
    are validated by these unit tests.
